Supplementary materials

### 2018-02-20 publication/supp_info.Rmd
Make chunks selfsufficient

```{r make figures per site}
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

site_plots_conspecific <- rlist::list.append(site_plots_conspecific, legend)
```

```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different sites."}
cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)
```

```{r figure per plant}
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name)) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

plant_plots_conspecific <- rlist::list.append(plant_plots_conspecific, legend)
```

```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across sites for different study species. Only species present in more than onse site are shown."}
cowplot::plot_grid(plotlist = plant_plots_conspecific, ncol = 3)
```

>>>>

```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different sites."}
loadd(dep_frame, sites)
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

site_plots_conspecific <- rlist::list.append(site_plots_conspecific, legend)

cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)

```

```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across sites for different study species. Only species present in more than onse site are shown."}
loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name)) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

plant_plots_conspecific <- rlist::list.append(plant_plots_conspecific, legend)

cowplot::plot_grid(plotlist = plant_plots_conspecific, ncol = 3)
```
